Stateless Model Checking with Data-Race Preemption Points

### 2016-07-14 oopsla-16/design.tex
reverse order of data-race-pps and choosing-best-job subsecs
forgot stupid changebar package breaks 2col tables

\cbstart
\subsection{Changing State Spaces}
\label{sec:algorithm0}

@@

{\bf Prioritizing smaller jobs.}
However, in tests where full verification is not feasible,
focusing on the maximal state space alone is likely to be fruitless.
%
Hence, we prioritize all subset jobs
\cbend
based on number of PPs, ETA, and whether they include data-race PPs,
We rely on state-space estimation \cite{estimation}
to predict which jobs are likely to complete within a reasonable time,
before actually testing a large fraction of interleavings for each.
The overall goal is to decide automatically when to defer testing a state space,
so an inexpert user can provide only their total CPU budget as a test parameter,
and to enable completing appropriately-sized jobs within that budget.
We seek to maximize completed state spaces,
as each one serves as a guarantee that all interleavings possible with its PPs were tested.
\cbstart
The next three subsections will show how we schedule these smaller jobs
based on their PP sets and ETAs.
\cbend

>>>>

\revisionx{
\subsection{Changing State Spaces}
\label{sec:algorithm0}

@@

{\bf Prioritizing smaller jobs.}
However, in tests where full verification is not feasible,
focusing on the maximal state space alone is likely to be fruitless.
%
Hence, we prioritize all subset jobs}
based on number of PPs, ETA, and whether they include data-race PPs,
We rely on state-space estimation \cite{estimation}
to predict which jobs are likely to complete within a reasonable time,
before actually testing a large fraction of interleavings for each.
The overall goal is to decide automatically when to defer testing a state space,
so an inexpert user can provide only their total CPU budget as a test parameter,
and to enable completing appropriately-sized jobs within that budget.
We seek to maximize completed state spaces,
as each one serves as a guarantee that all interleavings possible with its PPs were tested.
\revisionx{
The next three subsections will show how we schedule these smaller jobs
based on their PP sets and ETAs.
}
